MHF SCP Experiment Visualisations

### 2024-10-15 minos/outcomes/MHF_SCP_visualisations.Rmd
Quickly adding a summary function for UC and children population. Also added to the MHF_SCP_visualisations.Rmd script to add some calculations for the total eligible sample, as well as scaling the mental health risk results to a total E&W sample

```{r "mental_illness_risk_plots", include=FALSE}
mental_illness_risk_plots <- function(summary_group, scen.list, palette = my_palette) {

@@

@@

>>>>

```{r "mental_illness_risk_plots", include=FALSE}
mental_illness_risk_plots <- function(summary_group, scen.list, palette = my_palette, scale = scaling_factor) {

@@

# Sample Size Calculations

```{r}
# E&W adults: 48,566,000
# N: 160,908; 211,034
# N total: 371,942

# so we have
scaling_factor <- (371942 / 48566000) * 100
scaling_factor
```

@@

```{r}
summary_group <- 'men_illness_risk'
scen.list = scen.list.25_100

  print(p1)
  print(p2)
```
